%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Academic CV - Mario Torres Danta
% LaTeX Source Code
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% --- PREAMBLE ---
\documentclass[11pt, a4paper]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{palatino} % Palatino font
\usepackage[margin=0.8in]{geometry}
\usepackage{hyperref}         % Clickable links
\usepackage{titlesec}         % Section formatting
\usepackage{xcolor}           % Colors
\usepackage{microtype}        % Typography improvements
\usepackage{multicol}         % Multi-column layout
\usepackage{etoolbox}
\usepackage{textcomp} % For \textperiodcentered

% --- Color & Link Setup ---
\definecolor{darkblue}{HTML}{000033} 
\hypersetup{
	colorlinks=true,
	linkcolor=darkblue,
	urlcolor=darkblue,
	citecolor=black,
}

% --- Section Formatting ---
\titleformat{\section}
{\Large\bfseries\scshape\color{darkblue}}
{}
{0em}
{}[\color{darkblue}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

% --- Page Style ---
\pagestyle{empty}

% --- Custom List Command ---
\newcommand{\entry}[2]{\item[] \textbf{#1} \hfill \textit{#2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% --- DOCUMENT START ---
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
	
	% --- HEADER ---
	\noindent % Align left
	{\Huge \bfseries MARIO TORRES DANTA}
	\hfill % Push to right
	\parbox[t]{.4\textwidth}{\raggedleft \large
		(+34) 634 46 09 92 \\ 
		\href{mailto:martordan@alum.us.es}{martordan@alum.us.es} \\
		\href{https://github.com/mtdanta}{github.com/mtdanta} \\
		Seville, Spain
	}
	\vspace{6mm} % Vertical space
	
	% --- EDUCATION ---
	\section*{Education}
	\begin{itemize}
		\entry{B.Sc. in Mathematics}{2023 – 2027 (Expected)}
		\item[] \textit{University of Seville (US), Seville, Spain}
		\item[] \textbf{Current GPA: 8.78 / 10.0} (Based on 16 graded courses)
	\end{itemize}
	
	% --- ACADEMIC HONORS & DISTINCTIONS ---
	\section*{Academic Honors \& Distinctions}
	\begin{itemize}
		\item[] Awarded \textbf{"Matrícula de Honor" (Highest Distinction)} in 5 courses:
		\begin{multicols}{2}
			\begin{itemize}
				\item \textbf{General Topology (10.0)}
				\item \textbf{Measure Theory \& Lebesgue Integration (10.0)}
				\item \textbf{Numerical Analysis I (9.5)}
				\item \textbf{Ordinary Differential Equations (9.4)}
				\item \textbf{Probability Theory (9.4)}
			\end{itemize}
		\end{multicols}
		\item[] \textit{Additional "Sobresaliente" (A-Grade) in 5 courses (incl. Complex Analysis, Linear Algebra II, Discrete Mathematics).}
	\end{itemize}
	
	% --- RESEARCH EXPERIENCE ---
	\section*{Research Experience}
	
	% Current Project (2025-2026)
	\begin{itemize}
		\entry{Undergraduate Researcher (Alumno Interno)}{Sep 2025 - Jun 2026 (Current)}
		\item[] \textit{Department of Geometry and Topology, University of Seville}
		\item[] \textbf{Project:} Advanced topics in Topology and Group Theory. A guided study complementing the standard undergraduate curriculum.
		\item[] \textbf{Supervisor:} Prof. Ramón J. Flores
		\item[]	\textbf{------------------}
	\end{itemize}

	% Past Project (2024-2025)
	\begin{itemize}
		\entry{Undergraduate Researcher (Alumno Interno)}{Sep 2024 - Jun 2025}
		\item[] \textit{Department of Algebra, University of Seville}
		\item[] \textbf{Project:} Classification of homographies and homologies in real and complex projective spaces. \href{https://github.com/mtdanta/Academic-Work/tree/main/Projective-Geometry-Classification}{\color{darkblue}[View Project PDF \& Abstract]}
		\item[] \textbf{Supervisor:} Prof. Francisco Castro Jiménez
	\end{itemize}
	
	% --- RESEARCH INTERESTS ---
	\section*{Research Interests}
	\begin{itemize}
		\item[] Algebraic Topology (Homology, Cohomology, Homotopy Theory) \textperiodcentered{} Abstract Algebra (Group Theory, Ring Theory) \textperiodcentered{} Topological Data Analysis (TDA)
	\end{itemize}
	
	% --- ADVANCED INDEPENDENT STUDY ---
	\section*{Advanced Independent Study}
	\begin{itemize}
		\item[] Proactively self-studying \textbf{Munkres, "Algebraic Topology"} and \textbf{Sasho, "An Illustrated Introduction to Topology and Homology"}.
	\end{itemize}
	
	% --- SKILLS ---
	\section*{Skills}
	\begin{itemize}
		\item \textbf{Languages:} Spanish (Native), English (B2, C1 in preparation), French (B2)
		\item \textbf{Programming:} \textbf{Python} (Proficient; Certified by \textit{Santander Open Academy}), \textbf{SageMath} (Academic use)
		\item \textbf{Technical:} \textbf{\LaTeX{}} (Primary document preparation), \textbf{GitHub} (Repository management)
	\end{itemize}
	
	% --- REFERENCES ---
	\vfill % Push to bottom
	\begin{center}
		\textit{References (including research supervisors) and full academic transcript available upon request.}
	\end{center}
	
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% --- END OF DOCUMENT ---
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

